---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hdiffr

<!-- badges: start -->
<!-- badges: end -->

**hdiffr** performs an event history diffusion model that is modified in order to account for heterogeneity in the diffusion process. In addition to modeling characteristics that influnece the direct propensity of a focal actor to adopt, **hdiffr** can also model characteristics of the focal actor that make it more susceptible to the prior adoptions of other actors, as well as characteristics of prior-adopting actors that make them more or less influential on others, and characteristics of the social structure among actors that influence the transmission of influence between actors.

## Author

[Sang Won Han](https://sociology.columbia.edu/content/sang-won-han), Ph.D. candidate in [Sociology](https://sociology.columbia.edu/) at [Columbia University](https://www.columbia.edu)

## Reference

[Strang, David and Nancy Brandon Tuma. 1993. "Spatial and Temporal Heterogeneity in Diffusion." *American Journal of Sociology* 99(3): 614-639.](https://www.journals.uchicago.edu/doi/abs/10.1086/230318)

[Briscoe, Forrest, Abhinav Gupta, and Mark S. Anner. 2015. "Social Activism and Practice Diffusion: How Activist Tactics Affect Non-Targeted Organizations." *Administrative Science Quarterly* 60(2): 300-332.](https://journals.sagepub.com/doi/full/10.1177/0001839215579235?casa_token=C3NsMc_O3ZkAAAAA%3Ajs_seJ2S5xJIgFgkvDT56LZaqgSK-qgb8BFDQR6N9hmB95RlecbTMk-Xkb5Zkn0QB6fRD7xOWJBKK_w)

## Installation

The experimental version can be obtained via:

``` r
devtools::install_github("petershan1119/hdiffr")
```

## Example

This is a basic example which performs heterogeneous diffusion model with multispell data:

```{r example}
library(hdiffr)
data(exampleData)
result <- hdiffr(data = exampleData, xvars = c('lnsale', 'roa', 'vote'), vvars = 'activistgrp', wvars = 'lnsale', 
                 zgvars = 'sic', idvar = 'gvkey', multispell = 1, vintercept = 1, hrno = 1)
```

If you want to see the results, use `summary`:

```{r cars}
summary(result)
```
